Exploratory Plots

### 2020-09-11 exploratory/2020/sub3_fit_subsets.Rmd
Remove shapes

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset, shape=ref_weight)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```

>>>>

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```
